The Analog Method for Precipitation Downscaling: Finding Better Analog Situations at a Sub-Daily Time Step

### 2016-11-08 Moving temporal window - HESS/template.tex
Return to CRPS, RMSE and S1 in the text.

The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching analog situations for a target day starts by a preselection step of the potential candidate for analogy. Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects. Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score ($S_{\text{TW}}$), which is a comparison of gradients, over a certain spatial window and at certain hours. The smaller the $S_{\text{TW}}$ values, the more similar the pressure fields.

@@

Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate. Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day. This method will be named 2Z further on.

The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error ($E_{\text{RMS}}$) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}). This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations. When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.

@@

The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[$S_{\text{CRP}}$,][]{Brown1974, Matheson1976, Hersbach2000}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. It is defined as follows:

@@

In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference. The Continuous Ranked Probability Skill Score ($S_{\text{SCRP}}$) is thus defined as following:

\begin{equation}
\label{eq:CRPSS}
S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
\end{equation}
where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$). A better prediction is characterized by an increase in $S_{\text{SCRP}}$.

@@

Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the $S_{\text{TW}}$ criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW. The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day). The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better. An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogs are further improved. The latter effect is due to the accumulation of improvements brought by the new analog situations in the selection.

The improvements of the $S_{\text{TW}}$ criteria are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the $S_{\text{TW}}$ criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction. This confirms that all quantile seem similarly reduced ($S_{\text{TW}}$ distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig. \ref{fig:changes_S1} bottom).

@@

The impact of the MTW on the analogy criteria has been decomposed per precipitation classes. The results of this analysis are summarized in Fig. \ref{fig:changes_S1_precip_threshold} by the median reduction of $S_{\text{TW}}$ for days with precipitation (organized into classes) between two thresholds. The number of cases per class being reduced, the curves are not as smooth as in previous analyzes. It is nevertheless clear that the improvement tends to increase on days with higher precipitation. This is true for all our stations.

@@

A seasonal effect can be observed on the reduction of the $S_{\text{TW}}$ criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.

@@

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed. In contrast to earlier, both a reduction or an increase of the $E_{\text{RMS}}$ analogy criterion values are possible. Indeed, Fig. \ref{fig:changes_RMSE} shows an almost insignificant improvement of the $E_{\text{RMS}}$ values. Unlike for the first level of analogy, the relative improvement of the $E_{\text{RMS}}$ values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

@@

A systematic improvement of the $S_{\text{TW}}$ values was previously observed.

The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length. The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method. The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant. Moreover, it requires no additional predictor. No relationship was found between the improvement of the score and the reduction of the $S_{\text{TW}}$ criteria, neither with the season.

@@

The $S_{\text{TW}}$ criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect. \ref{sec:influence_precip}). The changes in terms of performance scores will now be assessed regarding precipitation thresholds. Fig. \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.

@@

The values of the $S_{\text{SCRP}}$ scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.

@@

The median of the $S_{\text{TW}}$ values reduction (Fig. \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one. This increasing trend with the analog rank can be explained by the accumulation of better analogs in the distribution. The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogs for every day of the calibration period. All other stations have a similar improvement of the $S_{\text{TW}}$ criteria, both in terms of distribution shape and amplitude.

@@

This result of a globally null improvement of the $E_{\text{RMS}}$ values does not mean that the 2Z-2MI method cannot be improved by the MTW. It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture. However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.

@@

It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs. As we saw in Fig. \ref{fig:changes_S1}, the improvement of the $S_{\text{TW}}$ criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions. It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values. The number of good analogs is thus globally increased.

@@

Table \ref{table:proxy_CRPSS} presents the $S_{\text{SCRP}}$ scores obtained by the reconstituted series using the proxy of precipitable water. A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost. A more recent reanalysis archive with more accurate moisture variables might produce better proxies.

@@

As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation. It has been here demonstrated that the improvement of the $S_{\text{TW}}$ criteria values is growing with the rank of the analog. This is due to the accumulation of better analogs within the predicted distributions.

@@

\begin{figure*}[htb]
	\begin{center}
		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
	\end{center}
	\caption{Changes in the $S_{\text{TW}}$ criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
	\label{fig:changes_S1_analogs}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the $S_{\text{TW}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the $S_{\text{TW}}$ distributions with and without the MTW. (b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
	\label{fig:changes_S1}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
	\end{center}
	\caption{Distribution of the median improvements of the $S_{\text{TW}}$ criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
	\label{fig:changes_S1_precip_threshold}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
	\end{center}
	\caption{Seasonal effect on the median reduction of the $S_{\text{TW}}$ criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
	\label{fig:changes_S1_seasons}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the $E_{\text{RMS}}$ criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the $E_{\text{RMS}}$ distributions with and without the MTW. (b) Quantiles of the relative improvements of the $E_{\text{RMS}}$ criteria when using the MTW.}
	\label{fig:changes_RMSE}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
	\caption{Differences of the $S_{\text{SCRP}}$ performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
	\label{fig:changes_CRPS_precip_threshold}
\end{figure}

@@

\begin{table}[htb]
	\caption{Parameters of the reference method on the atmospheric circulation (2Z). The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window). The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline 
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{$S_{\text{TW}}$} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{$E_{\text{RMS}}$} & \multirow{2}{*}{$N_{2}$} \\
			& TPW * RH850 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z-2MI}
\end{table}

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
			& $N_{1}$ & $S_{\text{SCRP}}$ & $N_{1}$ & $N_{2}$ & $S_{\text{SCRP}}$ \\ 
			\hline
			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:performance}
\end{table}

\begin{table}[htb]
	\caption{Influence of the archive reduction on the $S_{\text{SCRP}}$. $S_{\text{SCRP}}$ values are provided for both considered methods and the differences are expressed in absolute value.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
			\hline
			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:loss_reduction}
\end{table}

\begin{table}[htb]
	\caption{New $S_{\text{SCRP}}$ performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_MTW}
\end{table}

@@

\begin{table}[htb]
	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the newly calibrated parameters using the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Values of the $S_{\text{SCRP}}$ (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}

>>>>

The first method is based on the analogy of the atmospheric circulation only \citep[Table \ref{table:method_2Z},][]{Obled2002, Bontron2005, Marty2012}. Searching analog situations for a target day starts by a preselection step of the potential candidate for analogy. Here, it has been limited to the 4 months centered around the target date for every year of the archive, in order to cope with seasonal effects. Then, the similarity of the atmospheric circulation of the target date with every day of the preselection is assessed by processing the \citet{Teweles1954} score (S1), which is a comparison of gradients, over a certain spatial window and at certain hours. The smaller the S1 values, the more similar the pressure fields.

@@

Then, $N_{1}$ dates with the lowest values of S1 are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate. Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day. This method will be named 2Z further on.

The second reference method adds a subsequent level of analogy on moisture variables, compared by means of the root-mean-square error (RMSE) (method 2Z-2MI, Table \ref{table:method_2Z-2MI}). This second predictor is a moisture index made of the product of the total precipitable water (TPW) with the relative humidity at 850~hPa (RH850) \citep{Bontron2004}. When adding a second level of analogy, $N_{2}$ dates are subsampled in the $N_{1}$ analogs on the atmospheric circulation, to end up with a smaller number of analog situations. When a second level of analogy is added, a higher number of $N_{1}$ analogs is kept on the first level.

@@

The score that is most often considered to assess an AM performance is the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. It is defined as follows:

@@

In order to compare the value of the score in regard to a reference, one often considers its skill score expression, and use the climatological distribution as the reference. The Continuous Ranked Probability Skill Score (CRPSS) is thus defined as following:

\begin{equation}
\label{eq:CRPSS}
S_{\text{SCRP}} = \frac{S_{\text{CRP}}-S_{\text{CRP}}^{r}}{S_{\text{CRP}}^{p}-S_{\text{CRP}}^{r}} = 1-\frac{S_{\text{CRP}}}{S_{\text{CRP}}^{r}}
\end{equation}
where $S_{\text{CRP}}^{r}$ is the $S_{\text{CRP}}$ value for the reference (climatological distribution) and $S_{\text{CRP}}^{p}$ would be the one for a perfect prediction (which implies $S_{\text{CRP}}^{p}~=~0$). A better prediction is characterized by an increase in CRPSS.

@@

Figure \ref{fig:changes_S1_analogs} presents the changes in the distributions of the S1 criterion for the $1^{st}$, $5^{th}$, $20^{th}$ and $40^{th}$ analogs for the Ulrichen station on the whole calibration period, due to introduction of the MTW. The precipitation target remains as before, that is centered on 18~h~UTC (6~h~UTC to 6~h~UTC the next day). The shapes of the distributions of the conventional approach and the MTW are similar, but the values of the analogy criteria are now reduced (shifted to the left), and therefore better. An increase in the difference between a fixed window and a moving window is identifiable, which means that the last analogs are further improved. The latter effect is due to the accumulation of improvements brought by the new analog situations in the selection.

The improvements of the S1 criteria are summarized in Fig. \ref{fig:changes_S1}, which shows (top) quantiles of the S1 criteria according to the analog rank for the conventional method and the MTW, and (bottom) quantiles of the relative reduction. This confirms that all quantile seem similarly reduced (S1 distributions keep their shape), and that this improvement is constantly increasing from the first to the last analog (Fig. \ref{fig:changes_S1} bottom).

@@

The impact of the MTW on the analogy criteria has been decomposed per precipitation classes. The results of this analysis are summarized in Fig. \ref{fig:changes_S1_precip_threshold} by the median reduction of S1 for days with precipitation (organized into classes) between two thresholds. The number of cases per class being reduced, the curves are not as smooth as in previous analyzes. It is nevertheless clear that the improvement tends to increase on days with higher precipitation. This is true for all our stations.

@@

A seasonal effect can be observed on the reduction of the S1 criteria due to the MTW (Fig. \ref{fig:changes_S1_seasons}). The improvements are greater for winter than summer.

@@

When considering the second level of analogy of the 2Z-2MI method (Table \ref{table:method_2Z-2MI}), the number of candidates situations did not increase, as they are subsampled in the previously $N_{1}$ selected analogs, but their dates have changed. In contrast to earlier, both a reduction or an increase of the RMSE analogy criterion values are possible. Indeed, Fig. \ref{fig:changes_RMSE} shows an almost insignificant improvement of the RMSE values. Unlike for the first level of analogy, the relative improvement of the RMSE values are distributed relatively symmetrically around zero, with improvements and losses of the same amplitude. Once again, the results for the other stations are similar.

@@

A systematic improvement of the S1 values was previously observed.

The new performance scores are provided in Table \ref{table:CRPSS_MTW}, along with the differences regarding the conventional method with the same archive length. The differences ranges from 0.57 to 2.14 points for the 2Z method and from 1.53 to 2.20 points for the 2Z-2MI method. The introduction of the MTW brings an improvement of the performance that is not very large, but that is nevertheless significant. Moreover, it requires no additional predictor. No relationship was found between the improvement of the score and the reduction of the S1 criteria, neither with the season.

@@

The S1 criteria was previously found to be improved to a greater extent for the most dynamic situations related with higher precipitation values (Sect. \ref{sec:influence_precip}). The changes in terms of performance scores will now be assessed regarding precipitation thresholds. Fig. \ref{fig:changes_CRPS_precip_threshold} synthesizes these differences for the Ulrichen station, other stations having the same behavior.

@@

The values of the CRPSS scores for both methods (Table \ref{table:CRPSS_recalibration}) have significantly increased after recalibration.

@@

The median of the S1 values reduction (Fig. \ref{fig:changes_S1} bottom) starts approximately at 5~\% for the first analog and reaches more than 10~\% for the last one. This increasing trend with the analog rank can be explained by the accumulation of better analogs in the distribution. The minimum improvement starts from 0 and reaches 2--3\%, meaning that the criteria have been improved on most analogs for every day of the calibration period. All other stations have a similar improvement of the S1 criteria, both in terms of distribution shape and amplitude.

@@

This result of a globally null improvement of the RMSE values does not mean that the 2Z-2MI method cannot be improved by the MTW. It means that after the selection of the analogs situations in terms of the synoptic circulation, the new candidate dates do not allow to find better analogs in terms of moisture. However, the selected dates have changed in the first level of analogy, and thus also in the final selection, which can potentially improve the performance scores on the predictand.

@@

It seems as if the method perceive the increase in the archive length and diversity by allowing to extract more analogs. As we saw in Fig. \ref{fig:changes_S1}, the improvement of the S1 criteria grows along with the rank of the analog, which shows an accumulation of better analog situations in the distributions. It seems thus profitable to widen the selection of analogs in order to keep also some whose rank has increased, as they appear to be also relevant to predict precipitation values. The number of good analogs is thus globally increased.

@@

Table \ref{table:proxy_CRPSS} presents the CRPSS scores obtained by the reconstituted series using the proxy of precipitable water. A slight improvement can be obtained compared to the proportional distribution method, but it is still relatively small, and most of the benefit of the MTW is again lost. A more recent reanalysis archive with more accurate moisture variables might produce better proxies.

@@

As \citet{Finet2008} had previously shown, the introduction of a MTW allows finding better analog situations in terms of the atmospheric circulation. It has been here demonstrated that the improvement of the S1 criteria values is growing with the rank of the analog. This is due to the accumulation of better analogs within the predicted distributions.

@@

\begin{figure*}[htb]
	\begin{center}
		\includegraphics[width=15cm]{figures/changes_S1_analogues.pdf}
	\end{center}
	\caption{Changes in the S1 criteria distributions of (a) the $1^{st}$, (b) $5^{th}$, (c) $20^{th}$ and (d) $40^{th}$ analog ranks for the Ulrichen station, due to the MTW.}
	\label{fig:changes_S1_analogs}
\end{figure*}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.2cm]{figures/changes_S1_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the S1 criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the S1 distributions with and without the MTW. (b) Quantiles of the relative improvements of the S1 criteria when using the MTW.}
	\label{fig:changes_S1}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.3cm]{figures/changes_S1_precip_threshold.pdf}
	\end{center}
	\caption{Distribution of the median improvements of the S1 criteria, due to the MTW, depending on precipitation thresholds at the Ulrichen station.}
	\label{fig:changes_S1_precip_threshold}
\end{figure}

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=7cm]{figures/changes_S1_seasons.pdf}
	\end{center}
	\caption{Seasonal effect on the median reduction of the S1 criteria for the Ulrichen station due to the MTW. DJF: winter, MAM: spring, JJA: summer SON: fall.}
	\label{fig:changes_S1_seasons}
\end{figure}

@@

\begin{figure}[htb]
	\begin{center}
		\includegraphics[width=8.1cm]{figures/changes_RMSE_value_and_gain.pdf}
	\end{center}
	\caption{Synthesis of the changes in the RMSE criteria, due to the MTW, for the Ulrichen station, depending on the ranks of the analog. (a) Quantiles of the RMSE distributions with and without the MTW. (b) Quantiles of the relative improvements of the RMSE criteria when using the MTW.}
	\label{fig:changes_RMSE}
\end{figure}

\begin{figure}[htb]
	\includegraphics[width=5cm]{figures/changes_CRPS_precip_threshold.pdf}
	\caption{Differences of the CRPSS performance score, due to the introduction of the MTW, as a function of precipitation thresholds at the Ulrichen station. The stars represent averages.}
	\label{fig:changes_CRPS_precip_threshold}
\end{figure}

@@

\begin{table}[htb]
	\caption{Parameters of the reference method on the atmospheric circulation (2Z). The first column is the level of analogy (0 for preselection), then comes the meteorological variable and its hour of observation (temporal window). The criteria used for the current level of analogy is then provided, as well as the number of analogs.}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z}
\end{table}

\begin{table}[htb]
	\caption{Parameters of the reference method with moisture variables (2Z-2MI). Same conventions as Table \ref{table:method_2Z}}
	\footnotesize
	\begin{center}
		\begin{tabular}{ccccc}
			\hline 
			Level & Variable & Hour & Criteria & Nb \\ 
			\hline 
			0 & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z1000 & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{$N_{1}$} \\
			& Z500 & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH850 & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{$N_{2}$} \\
			& TPW * RH850 & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:method_2Z-2MI}
\end{table}

\begin{table}[htb]
	\caption{Number of analogs (of the first and the second level of analogy, respectively $N_{1}$ and $N_{2}$) and skill score (\%) of the method based on the atmospheric circulation only (method 2Z), and the one with a second level of analogy on moisture variables (2Z-2MI), on the full archive.}
	\begin{center}
		\begin{tabular}{l c c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{3}{c}{2Z-2MI} \\
			& $N_{1}$ & CRPSS & $N_{1}$ & $N_{2}$ & CRPSS \\ 
			\hline
			Ulrichen & 40 & 30.73 & 60 & 25 & 34.31 \\
			Zermatt & 35 & 23.87 & 55 & 25 & 28.28 \\
			Visp & 30 & 25.11 & 45 & 25 & 28.85 \\
			Montana & 40 & 32.55 & 55 & 30 & 36.11 \\
			Sion & 40 & 26.23 & 90 & 30 & 31.16 \\
			Aigle & 50 & 30.59 & 100 & 35 & 35.82 \\ 
			\hline
		\end{tabular}
	\end{center}	
	\label{table:performance}
\end{table}

\begin{table}[htb]
	\caption{Influence of the archive reduction on the CRPSS. CRPSS values are provided for both considered methods and the differences are expressed in absolute value.}
	\begin{center}
		\begin{tabular}{l c c c c }
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& 82-07 & $\Delta$ & 82-07 & $\Delta$ \\ 
			\hline
			Ulrichen & 29.37 & -1.36 & 33.24 & -1.08 \\
			Zermatt & 22.20 & -1.67 & 26.95 & -1.32 \\
			Visp & 23.23 & -1.89 & 27.77 & -1.08 \\
			Montana & 30.79 & -1.76 & 34.77 & -1.34 \\
			Sion & 24.78 & -1.45 & 29.36 & -1.80 \\
			Aigle & 30.57 & -0.01 & 35.95 & 0.13 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:loss_reduction}
\end{table}

\begin{table}[htb]
	\caption{New CRPSS performance scores for both 2Z and 2Z-2MI methods obtained by the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.12 & 1.74 & 35.44 & 2.20 \\
			Zermatt & 24.34 & 2.14 & 28.92 & 1.97 \\
			Visp & 24.39 & 1.16 & 29.42 & 1.64 \\
			Montana & 31.59 & 0.80 & 36.30 & 1.53 \\
			Sion & 25.35 & 0.57 & 31.07 & 1.71 \\
			Aigle & 31.78 & 1.21 & 38.11 & 2.16 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_MTW}
\end{table}

@@

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the newly calibrated parameters using the MTW approach. The differences are expressed regarding the conventional method with the same archive length.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& MTW & $\Delta$ & MTW & $\Delta$ \\
			\hline
			Ulrichen & 31.58 & 2.20 & 35.72 & 2.48  \\
			Zermatt & 24.71 & 2.51 & 29.63 & 2.68 \\
			Visp & 25.08 & 1.85 & 30.29 & 2.52 \\
			Montana & 32.22 & 1.43 & 37.15 & 2.38 \\
			Sion & 26.07 & 1.29 & 31.68 & 2.32 \\
			Aigle & 32.21 & 1.64 & 38.50 & 2.55 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Values of the CRPSS (\%) skill score for the original and the recalibrated parameters (with the sequential method, as described in Sect. \ref{sec:introduction}) using the MTW approach on the disaggregated precipitation time series (short period) by means of the proportional distribution.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{ 2}{c}{2Z-2MI} \\
			& original & recalib. & original & recalib. \\
			\hline
			Ulrichen & 29.13 & 29.61 & 33.15 & 33.45 \\
			Zermatt & 22.17 & 22.80 & 26.72 & 27.43 \\
			Visp & 22.32 & 22.89 & 27.01 & 28.04 \\
			Montana & 29.41 & 30.24 & 33.83 & 34.55 \\
			Sion & 22.98 & 23.41 & 28.57 & 29.15 \\
			Aigle & 29.07 & 29.46 & 34.66 & 35.09 \\
			\hline
		\end{tabular}
	\end{center}
	\label{table:disaggregation_proportional}
\end{table}
